\cvsection{Education}

\cvevent{PhD, Probability and Mathematical Physics}{University of Warwick}{Oct 2019 -- September 2022}{}
\medskip
Conducted original research at the interface of Probability Theory, Statistical Mechanics and Quantum Field Theory. \\
\smallskip
{\bf Published work:}
\medskip
\begin{itemize}
    \item A multivariate extension of the Erd\"os-Taylor theorem. \href{https://arxiv.org/abs/2202.08145}{ \fontfamily{cmtt}\selectfont arxiv:2202.08145}, (under revision at {\em Probability Theory and Related Fields}).

    \item Moments of the $2d$ directed polymer and a generalisation of the Erd\"os - Taylor theorem,
        {\em Commun. Math. Phys.} (2023). \href{https://link.springer.com/article/10.1007/s00220-023-04694-w}{(journal link)}. ({\bf 10 citations})

    \item Edwards-Wilkinson fluctuations for the directed polymer in the full $L^2$-regime for dimensions $d \geq 3$, {\em Ann. Inst. H. Poincaré Probab. Statist.} (2022), \href{https://projecteuclid.org/journals/annales-de-linstitut-henri-poincare-probabilites-et-statistiques/volume-58/issue-1/EdwardsWilkinson-fluctuations-for-the-directed-polymer-in-the-full-L2/10.1214/21-AIHP1173.short}{(journal link)}. ({\bf 25 citations})

\end{itemize}


\bigskip


\cvevent{MSc, Mathematics and Statistics}{University of Warwick}{Oct 2018 -- Sept 2019}{}

\begin{itemize}
    \item Part of a 4-year funded PhD studentship, MASDOC DTC, University of Warwick, 2018.
    \item Awarded with distinction.
\end{itemize}
\smallskip
{\bf Focus areas}: \\
\smallskip
PDE, Bayesian Statistics, Stochastic Processes, Statistical Physics.

\bigskip

\cvevent{BSc, Pure \& Applied Mathematics}{University of Athens}{Oct 2014 -- August 2018}{}
\begin{itemize}
    \item GPA: 8.9/10
    \item Admitted {\bf 1st} among all candidates with score {\bf 19.532/20} in the national examinations.
\end{itemize}

