\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[11pt,a4paper]{altacv}
%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}
%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{ragged2e}
\definecolor{cadmiumgreen}{rgb}{0.0, 0.42, 0.24}
\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}\definecolor{dukeblue}{rgb}{0.0, 0.0, 0.61}
\definecolor{gg}{rgb}{0.47, 0.09, 0.29}
%Colors

\definecolor{accent}{HTML}{000066}
\definecolor{heading}{HTML}{000000}
\definecolor{emphasis}{HTML}{666699}
\definecolor{body}{HTML}{000000}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}



\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=dukeblue,      
    urlcolor=dukeblue,
}
\urlstyle{same}

\begin{document}
\name{Dimitrios Lygkonis}
\tagline{Software Engineer}
\personalinfo{
    \printinfo{\faBirthdayCake}{8th Feb 1996}
    \email{\texttt{dimitris.ligonis@gmail.com}}
    \location{London, UK}
}

%

\begin{fullwidth}
    \makecvheader
\end{fullwidth}

%
\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Software Engineer}{FINBOURNE Technology}{October 2022 -- October 2023}{London, UK}
\medskip

    Part of the {\bf Analytics} team. \medskip

    \begin{itemize}
        \setlength\itemsep{1em}
    \item {Contributed to the {\it development}, {\it monitoring} and {\it maintenance} of a distributed computing grid.} \\
          \smallskip
          \begin{itemize}
              
              \item[$\circ$] Built logging infrastructure handling 1 million trace logs per day, with 99.9\% uptime. 
              
              Stack: {\bf Kafka/Elastic Search}
              
              \item[$\circ$] Designed and implemented a scripted translation service for financial entities handling 50 thousand requests a day that helped onboard new clients.
              
              Stack: {\bf .NET/PostgreSql/JavaScript/XSLT}

              \item[$\circ$] Developed, deployed and maintained distributed {\bf.NET} microservice applications integrating market data providers as well as serving internal functionality using {\bf RabbitMQ} for messaging, {\bf Redis} for distributed rate limiting.
              
              \item[$\circ$] Created pipelines covering all {\bf CI/CD} stages.
              
              Stack: {\bf Kubernetes}/{\bf Concourse}/{\bf Helm}
                        
          \end{itemize}

\end{itemize}
\cvsection{Skills}

\begin{itemize}
    \item {\bf Software Development:} 
    \smallskip
    \begin{itemize}
        \item[$\circ$] .NET, Python, Bash, PostgreSql, JavaScript, XSLT
    \end{itemize}
    \smallskip
    \item {\bf DevOps:} 
    \smallskip
    \begin{itemize}
        \item[$\circ$] Kubernetes, Helm, Concourse, Prometheus, Loki
    \end{itemize}
    \smallskip
    \item {\bf Data pipelines/storage :} 
    \smallskip
    \begin{itemize}
        \item[$\circ$] Kafka, RabbitMQ, Redis, Elastic Search, S3 
    \end{itemize}
    
\end{itemize}


\medskip


\cvsection{Interests}
\justifying I enjoy playing with computer systems outside work. During my spare time, I am maintaining a small Kubernetes cluster at home, using ArgoCD/ArgoWorkflows for CI/CD. I enjoy doing projects that involve modelling advanced concepts in distributed computing with toy model services and APIs for personal use and fun.

\smallskip
I also love art. In my free time I enjoy playing music (string instruments), watching films and going to the theatre. 



\medskip
\cvsection{Languages}
\begin{itemize}
    \item[$\circ$]  \textbf{\textcolor{emphasis}{English}}\hfill (fluent)
    \item[$\circ$]  \textbf{\textcolor{emphasis}{Greek}}\hfill (native) 
\end{itemize}
\medskip

\end{document}
